---
title: "{{cookiecutter.project_name}} Vignette"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{{{cookiecutter.project_name}} Vignette}
    %\VignetteEngine{rmarkdown::html_vignette}
    %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# This is a Mock Vignette
- Manuscripts written within `{{cookiecutter.__project__slug}}_rtools` are converted to HTML 
using `pkgdown` and published at [https://{{ cookiecutter.__project_slug }}.readthedocs.io/en/latest/r_api/](https://{{ cookiecutter.__project_slug }}.readthedocs.io/en/latest/r_api/).
- Because these files are somewhat isolated from the documentation built by Sphinx, 
we do not actively recommend creating vignettes other than standard `.R` script documentation (e.g., using `roxygen2`). 
(You can achieve the same functionality using `.ipynb` files, which can be integrated and built seamlessly with Sphinx).
- However, as demonstrated in this file, you can still add a vignette by creating an `.Rmd` file 
and including the following YAML header tags:
    ````yaml
    ---
    title: "Vignette Name"
    output: rmarkdown::html_vignette
    vignette: >
        %\VignetteIndexEntry{Vignette Name}
        %\VignetteEngine{rmarkdown::html_vignette}
        %\VignetteEncoding{UTF-8}
    ---

    ```{r setup, include=FALSE}
    knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
    )
    ```
    ````
- Like any other `.Rmd` file, you can write your content using 
standard Markdown (`.md`) syntax while embedding R code inside code blocks. 
Please use this feature for purposes such as creating tutorials for your R scripts.

## Example
---
## Polynomial Ring
```{r}
_sca_ <- function (a, f) {
  function(x) a * f(x)
}

_add_ <- function (fp, fq) {
  function(x) fp(x) + fq(x)
}

_mul_ <- function (fp, fq) {
  function(x) fp(x) * fq(x)
}

f1 <- function (x) {
  x
}

f2 <- function (x) {
  x ^ 2
}

v <- 1234
w <- 5678
```

### Scalar Multiplication
- Closure
```{r}
typeof(_add_(f1, f2)(v))
typeof(_add_(f1, f2)(w))
```

### Summation
- Closure
```{r}
typeof(_add_(f1, f2)(v))
typeof(_add_(f1, f2)(w))
```

- Commutativity
```{r}
_add_(f1, f2)(v) == _add_(f2, f1)(v)
_add_(f1, f2)(w) == _add_(f2, f1)(w)
```

- Associativity
```{r}
_add_(_add_(f1, f2), f3)(v) == _add_(f1, _add_(f2, f3))(v)
_add_(_add_(f1, f2), f3)(w) == _add_(f1, _add_(f2, f3))(w)
```

- Identity Element
```{r}
fis <- function (x) {
  0
}
_add_(f1, fis)(v) == f1(v)
_add_(f1, fis)(w) == f1(w)
_add_(f2, fis)(v) == f2(v)
_add_(f2, fis)(w) == f2(w)
```

- Inverse Element
```{r}
get_inverse <- function (f) {
  _sca_(-1, f)
}
_add_(f1, get_inverse(f1))(v) == fis(v)
_add_(f1, get_inverse(f1))(w) == fis(w)
_add_(f2, get_inverse(f2))(v) == fis(v)
_add_(f2, get_inverse(f2))(w) == fis(w)
```

### Multiplication
- Closure
```{r}
typeof(_mul_(f1, f2)(v))
typeof(_mul_(f1, f2)(w))
```

- Commutativity
```{r}
_mul_(f1, f2)(v) == _mul_(f2, f1)(v)
_mul_(f1, f2)(w) == _mul_(f2, f1)(w)
```

- Associativity
```{r}
_mul_(_mul_(f1, f2), f3)(v) == _mul_(f1, _mul_(f2, f3))(v)
_mul_(_mul_(f1, f2), f3)(w) == _mul_(f1, _mul_(f2, f3))(w)
```

- Identity Element
```{r}
fim <- function (x) {
  1
}
_mul_(f1, fim)(v) == f1(v)
_mul_(f1, fim)(w) == f1(w)
_mul_(f2, fim)(v) == f2(v)
_mul_(f2, fim)(w) == f2(w)
```

---
This project was created with [Cookiecutter](https://github.com/cookiecutter/cookiecutter) 
and [BasalCell](https://github.com/yo-aka-gene/BasalCell) version {{cookiecutter.__version}}
